---
title: "Twitter Sentimental Analysis"
output: 
    html_document:
        smart: false
---

## Following steps to be followed
* Create Twitter app and get the credentials
* You will get consumer token
* Generate API Token

#### Two package is required for autheticating with twitter for R
* twitteR -> For twitter data
* ROAuth  -> For authentication 

For R code use authentication.R file

#### Below code is used for authenticating the data
```{r "twitter tokens"}
#install.packages(c("twitteR","ROAuth"))
library(twitteR)
library(ROAuth)

consumer.token <- 'CWpVX762aYsmM7AzlRYQZEXO2'
consumer.secret <- 'Gggt6BP2AD5tqJYGLCbPgYkKlZvg5XLTle2ssiJNGZhsTpuI1S'
api.token <- '396442752-iPq6G6AnkYpxJ7fKZfpcbilcOjimQrNfQ3CK1HI7'
api.secret <- 'fUMySwMTFVNrfiki5eKjc5YgrI7AcAAuGP3KZQ8P5JWJT'

```

#### Download the certificate for the For storing pem file


```{r "Download pem file and create credentials"}
download.file(url = "http://curl.haxx.se/ca/cacert.pem", destfile = "cacert.pem") #downloads the certificate

setup_twitter_oauth(consumer.token, consumer.secret, api.token, api.secret)

cred <- OAuthFactory$new(consumerKey = consumer.token,
    consumerSecret = consumer.secret,
    requestURL = 'https://api.twitter.com/oauth/request_token',
    accessURL = 'https://api.twitter.com/oauth/access_token',
    authURL = 'https://api.twitter.com/oauth/authorize')
```

### We have to data Preparation


#### Descriptive Statistics

Here we will be working on Trum tweets

```{r "Download and analysis data"}

```
